\documentclass[12pt]{article}
\usepackage{tabularx}
\begin{document}
\title{Computer Science 130, Homework 1}
\date{April 17th, 2019}
\author{Michael Wu\\UID: 404751542}
\maketitle

\section{Introduction}

\subsection{Purpose}

We will create a application that helps customers find good restaurants and reserve tables at them.
This application will combine features from Yelp and OpenTable to ensure that users are able to find the best
restaurants. Currently Yelp's system is biased because restaurant owners can pay to have their restaurant listed
higher or appear better than their competitors. This process is detrimental to the customer experience, since the
best restaurants do not get the recognition they deserve. Our application will not allow this so that our customers
know they are getting the most accurate reviews. Yelp also does not have a reservation system, so when users find
a restaurant they like they have to call to make a reservation. Our platform will allow reservations
directly within the application to avoid this inconvenience. Restaurants will also be able to manage their reservations better
on our platform. Our system will be available as both a mobile application and a web application.

\subsection{Intended Audience}

Our intended audience is customers who are actively looking for restaurants, and restaurant owners that want to
increase their publicity. Both these groups would benefit from this application since customers would receive better
restaurant results while owners will receive more customers. We will also set up an interface for our own administrators
in order to manage customer and restaurant accounts.

\subsection{Intended Use}

The customers will create accounts to use our application to search for restaurants that are highly rated. They are
able to search by location, cuisine type, price range, restaurant name, or specific food items. When they find a restaurant, they can
view more information such as a description, reviews, pictures, hours, contact information, and a button to make reservations.
When the user clicks the reservation button, they can select a given time and the reservation request will be sent to the restaurant.
Users can leave reviews with a score and text on a restaurant's profile.

Restaurant owners will create accounts prior to being listed with our platform. In the restaurant owner interface they can upload
data about their business such as contact information, pictures, and hours. They also have a system to manage reservations and
will receive any reservation requests from customers. They can confirm or cancel reservations inside our application.

\subsection{Scope}

Our application will consist of a mobile application and a web portal. Customers and restaurant owners can log into accounts
on these platforms that allow them to use the review and reservation system. We plan to first launch this service within the United States,
and it would include all categories of restaurants. Even if a restaurant does not take reservations, we would include it within our service.
This way we can have a wider appeal as there is more variety in restaurants. We will not try to include extra features such as ordering
for delivery in our initial build, as these can be developed later.

\section{Overall Description}

\subsection{Product Perspective}

Our product should allow customers to simplify the restaurant finding process. It makes it easy to find unbiased reviews and make
reservations at a restaurant. Restaurant owners will also use our platform to seamlessly manage reservations and upload information
to promote their restaurants.

\subsection{User Needs}

The main user need is to easily find quality restaurants with minimal hassle. They must have confidence that the reviews on our
platform will be accurate and reliable. Additionally the user should be able to find most restaurants through our service, since
we do not want to leave any good restaurants out. Users also need to be able to make reservations with the click of a button so that their
dining experience is seamless. The response time of our reservation system should be fast.

For restaurant owners, our platform needs to make it easy to set up their restaurant profile and reservation system. We should
help them learn how to use our application and make it easy to upload information about their business.

We also need method for administrators on our end to detect and delete spam accounts or fraudulent reviews.

\subsection{Assumptions and Dependencies}

We assume that customers will be able to call a restaurant if they are unable to confirm a reservation. Since we will not implement
a messaging system, customers may be confused about why a reservation is declined. In this case only a call can resolve this issue.
Additionally, we assume that restaurants will integrate our platform's reservation system with their current reservation system.

\subsection{Constraints}

Our application requires internet connectivity, so it may not work if either a customer or restaurant has no internet. We also
want our servers to be available as much as possible so that our service does not experience outages. This means that we should
implement a way to test and deploy changes to our service without interrupting our production build.

\section{System Features and Requirements}

\subsection{Functional Requirements}

\begin{center}
    \begin{tabularx}{\linewidth}{c|c|X}
        User Class & Title & Description\\
        \hline
        \hline
        Customer & Search & Restaurants can be found by location, cuisine type, price range, name, or specific food items.\\
        \hline
        Customer & Review System & People can leave and view reviews of restaurants. Users that leave many quality reviews will have theirs shown first.\\
        \hline
        Customer & Reservation System & People should be able to schedule a reservation with a restaurant and have that restaurant confirm the reservation.\\
        \hline
        Customer & Location Finder & Our platform should recommend nearby restaurants using some sort of location services.\\
        \hline
        Customer & Account Management & Customers can see their account info to see past reviews, change their password, etc.\\
        \hline
        Owners & Business Profile & Restaurant owners should be able to manage their business info and reservation list.\\
        \hline
        Admins & Moderation System & Admins should have an interface to remove unwanted spam and fake accounts.\\
        \hline
        Admins & Spam Detection & We should have some automated flagging system to mark potential spam and fake accounts.
    \end{tabularx}
\end{center}

\subsection{External Interface Requirements}

\subsubsection{User Interface}

The main user interface will be both a mobile application and a web application. The mobile application should work on iOS
and Android, as these are the most widely used mobile platforms.

\subsubsection{Hardware Interface}

We will set up a web server to store the information that we collect in a database. This can be either in the cloud on in
a data center that we set up ourselves. Our mobile and web clients will communicate with these over the internet.

\subsubsection{Software Interface}

Our web server will have API calls that enable users to perform actions that retrieve or modify the information in our database.
These calls must include authentication information.

\subsubsection{Communication Interface}

Our client software will make API calls to our database in order to send and retrieve information over the internet. Without
internet our application will simply show an error message

\subsection{System Features}

Other features that were not already mentioned in the functional requirements include a set of tutorial messages that
helps owners and customers learn how to use our application.

\subsection{Nonfunctional Requirements}

\begin{center}
    \begin{tabularx}{\linewidth}{c|X}
        Title & Description\\
        \hline
        \hline
        Scalability & Our service performance should scale reasonably as the number of users and restaurants increase. Our service architecture should be easily expandable.\\
        \hline
        Speed & Our service should be able to send and receive data with minimal delay.\\
        \hline
        Uptime & Our service should stay available at all times if possible. We should not have to take our servers down often for maintenance.\\
        \hline
        Reliability & Our service should store data in multiple locations in order to prevent loss of data. It should also work as expected and have minimal errors.
    \end{tabularx}
\end{center}

\subsection{Design Constraints}

The main constraints on our development come from limited budget and developer time. We cannot begin working with a large team, so we must find
ways to prototype our application with a small team with a single server. Afterwards we can scale up our development with multiple servers
and a larger database before releasing our application.

\section{Change Management Process}

Changes will go through the client Aashika. For each change we will have a meeting and
draft a change proposal in order to document the reasons why we are making a change. During
our change meetings we will also specify the additional costs of making a change.

\end{document}`